---
title: "Introduction to R"
author: "Gustavo Magaña López"
date: "4/26/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[R](https://www.r-project.org/) is a free software environment for statistical computing and graphics. It compiles and runs on a wide variety of UNIX platforms, Windows and MacOS. 


## Used packages
When working with R, we can define our own functions and create modules called packages which serve a specific purpose. These can be submitted to [CRAN](https://cran.r-project.org/)(The Comprehensive R Archive Network). Publishing a package enables people to use the code you have developed!
In this case we are using the following packages:
```{r imports, message=FALSE, warning=FALSE}
library(ggplot2)
library(lubridate)
library(reshape2)
```

## Reproducibility
In order for you to reproduce the results found in this notebooks, we must set a seed for the random number generator. This is a topic beyond the scope of this repo, but I highly advise you to read about [pseudorandom number generators](https://en.wikipedia.org/wiki/Pseudorandom_number_generator).
```{r seed, message=FALSE, warning=FALSE}
  set.seed(204) # so you can reproduce the results
```




